Evaluate PEER in each cohort and brain region

### 2020-11-23 combined_analysis/eval_resid_in_each.Rmd
add CTS

```{r}
# create new parent folder for these results
CODE <- Folder(name = "CTS - Evaluate PEER in each cohort and brain region", parentId = "syn23567522")
CODE <- synStore(CODE)

>>>>

```{r create.folder.2}
# create new parent folder for these results
CODE <- Folder(name = "CTS - Evaluate PEER in each cohort and brain region", parentId = "syn23567522")
CODE <- synStore(CODE)
